---
title       : Data Produts
subtitle    : Report
author      : Wolfgang Gross
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## First Steps 

First I started with:

1. Getting the Data of twitter
2. looking into the data (1,7 GB)
3. Find I need a prepreocessing -  couldn't do wihin R
4. Write a small programm reading and cleaning the raw dat in .NET Framework


---
## Data in R
Load and save Data

```{r,echo=TRUE,results='hide',message=FALSE}
library(ggplot2)
library(bit64)
df1 <- readRDS(file="plot_second.Rda")
df2 <- readRDS(file="plot_minute.Rda")
df3 <- readRDS(file="plot_hour.Rda")
```

---

## Working on the Data
The Data contained:

* TwitterID
* UserId
* Timestamp
* Latitude and Longitue
* Country or City
* Content of the Tweet

---
## Working on the Data
Count Number of tweets for ervery timestepp.

Sum up for every Minute and Hour.

```{r,eval=FALSE}
count  <- data.frame(table(dat$V3))
sumMinute <- c()
for(i in seq(1,length(count$Freq),60)){sumMinute <- append(sumMinute,sum(count$Freq[i:(i+60)]))}
sumHour <- c()
for(k in seq(1,length(count$Freq),3600)){sumHour <- append(sumHour,sum(count$Freq[k:(k+3600)]))}
realTime <- strptime(as.character(count$Var1),format="%Y%m%d%H%M%S")
```

---
## Plot Data
For ploting the Data I used ggplot
```{r,eval=FALSE}
df <- data.frame(realTime,Tweet.count)
ggplot(df,aes(x=realTime,y=Tweet.count)) + geom_line()
```

---
## Tweets per Second - Minute - Hour
Plot wiht different time resolutions

```{r,echo=FALSE, fig.width=4,fig.height=6,warning=FALSE}

ggplot(df1,aes(x=time,y=count)) + geom_line()

ggplot(df2,aes(x=time,y=count)) + geom_line()

ggplot(df3,aes(x=time,y=count)) + geom_line()

```
